### 2023-11-22 Scripts/Manuscript/manuscript.Rmd
removed warning messages in manuscript pdf, and improved the placement of floats.

@@

\renewcommand{\arraystretch}{0.7}

```{r QMPCodingInfoTable}
QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
           'Example Question' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for a true rating).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

# transfer the data to an APA table for printing
apa_table(
  QMP_info_dataframe, align = c("l", "r", "l")
  , caption = "Information of QMP coding variables per category."
  , note = "N Questions refers only to the questions considered quantative as specified in the text below."
  , escape = FALSE, placement= "ht", booktabs = TRUE)

@@

```{r Check for Reliability and Validity Testability, include = FALSE}
## Checking the measures to recalculate the reliability and factor analysis for.
## The question: "Are they psychometrics scales or not?", is key here.
View(coded_data_replications)

@@

```{=tex}
\begin{align}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
\end{align}
```
```{r Hypothesis 2 Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

@@

```{r ReplicationRatioTable}
# construct the replication ratio table to be printed
replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))

@@

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the thesis"
  , escape = FALSE, placement = "ht", midrules = 4)

@@

```{r Plot23AlphaCode, fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from."}
# plot for alpha
ggplot(plot_23_data_alpha, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 6.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 7, ymax = 7, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Cronbach's alpha")

@@

```{r ReplicabilityReliabilityTestTable}
# creating the dtaframe for the table
H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)

@@

# print the table in apa formatting
apa_table(
  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
  , caption = "Model Results from Tests of Hypothesis 3"
  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively. The random slope model for Cronbach's alpha did not converge, thus it results are not shown here. $^* p < .05$"
  , escape = FALSE, placement= "ht", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))

@@

```{r Plot456Code, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by where each was coded from. The top row shows binned counts of QMP ratio’s that were observed for each replication protocol and original article, across the different QMP types. The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio. The specific observed values are indicated along the bottom row with dots"}
# plot for alpha
### ratio (REV) Original and Rep
Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
       aes(x = QMP_ratio, fill = RepOrg)) + 
  geom_bar(position = "dodge", stat = "bin", bins = 10) +
  facet_grid(~QMP_type) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_manual(values=c("brown", "blue4")) +
  theme(legend.position = "none") +
  ylab("Count") +
  xlab("QMP Ratio") +
  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

@@

```{r Plot46RevisedDataCode, error = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line. The abbreviations on the axes relate to the QMP categories described in Table 1: Def. is definition, Op. is operationalization, Sel. is selection/creation, Quant. is quantification, and Mod. is modification. The X axis facets across the QMP ratios in the original articles, and the Y axis facets across the QMP ratios in the replication protocols. Each dot in the figure relates to describes the QMP ratio for the types in that graph across an original article and its replication protocol. Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
# Revised
ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

```{r H6ExploratoryAssociationsRevisedTable}
# creating the dataframe for the table
H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
  Results_H6_between_REV$sel_mod)

@@

# print the table in apa formatting
apa_table(
  H6_table_REV_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
  , caption = "Beta Regression Test Results for the Association between Replication
QMP Ratio and Original QMP Ratio as obtained using the Revised Protocol"
  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type. Sample size for comparisons involving modification were lower since not all measures were modified. Therefore the standard errors are larger. $^* p < .05$"
  , escape = FALSE, placement= "ht", midrules = c(1, 6, 7, 12, 13))

@@

```{r H6ExploratoryAssociationsInitialTable}
# creating the dataframe for the table
H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
  Results_H6_between$sel_mod)

@@

# print the table in apa formatting
apa_table(
  H6_table_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
  , caption = "Beta Regression Test Results for the Association between Replication
QMP Ratio and Original QMP Ratio as obtained using the Initial Protocol"
  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type. Sample size for comparisons involving modification were lower since not all measures were modified. Therefore the standard errors are larger. $^* p < .05$"
  , escape = FALSE, placement= "ht", midrules = c(1, 6, 7, 12, 13))

@@

```{r UnidimesnionalityTestResultsTable}
# add the names of the relevant papers and a shortcut for the measure used.
cfa_results_expanded <- cbind(c("Caruso et al. (2012)", "Husnu & Crisp (2010)", "Nosek et al. (2002), Art", "Nosek et al. (2002), Math", "Van Lange et al. (1997)", "Anderson et al. (2012), SWL", "Anderson et al. (2012), PA", "Anderson et al. (2012), NA", "Giessner & Schubert (2007)", "Norenzayan et al. (2002)", "Zhong & Liljenquist (2006)", "Monin & Miller (2001), most", "Monin & Miller (2001), some", "Cacioppo et al. (1983), elm", "Cacioppo et al. (1983), nfc", "De Fruyt et al. (2000), consc", "Albarracín et al. (2008), exp. 5", "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)

@@

# print the table in apa formatting
apa_table(
  cfa_results_for_print, align = c("l", "r", "r", "r")
  , caption = "RMSEA and Parallel Analysis Suggested Factors based on Factor Analysis
for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data. The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "ht")

>>>>

<!-- altering latex defaults to get better figure and table placement -->
\renewcommand{\arraystretch}{0.7} <!-- reducing the line spacing within tables -->
\renewcommand{\topfraction}{.85} <!-- max fraction of page for floats at top -->
\renewcommand{\bottomfraction}{.7} <!-- max fraction of page for floats at bottom -->
\renewcommand{\textfraction}{.15} <!-- min fraction of page for text -->
\renewcommand{\floatpagefraction}{.66} <!-- min fraction of page that should have floats -->
\setcounter{topnumber}{3} <!-- max number of floats at top of page -->
\setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page -->
\setcounter{totalnumber}{4} <!-- max number of floats on a page -->
<!-- remember to use [htp] or [htpb] for placement -->

@@

```{r QMPCodingInfoTable, warning = FALSE}
QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
           'Example Question' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for a true rating).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

# transfer the data to an APA table for printing
apa_table(
  QMP_info_dataframe, align = c("l", "r", "l")
  , caption = "Information of QMP coding variables per category."
  , note = "N Questions refers only to the questions considered quantative as specified in the text below."
  , escape = FALSE, placement= "htp", booktabs = TRUE)

@@

```{r Check for Reliability and Validity Testability, include = FALSE, warning = FALSE}
## Checking the measures to recalculate the reliability and factor analysis for.
## The question: "Are they psychometrics scales or not?", is key here.
View(coded_data_replications)

@@

```{=tex}
\begin{align}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
\end{align}
```

```{r Hypothesis 2 Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

@@

```{r ReplicationRatioTable, warning = FALSE}
# construct the replication ratio table to be printed
replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))

@@

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the thesis"
  , escape = FALSE, placement = "htp", midrules = 4)

@@

```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from."}
# plot for alpha
ggplot(plot_23_data_alpha, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 6.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 7, ymax = 7, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Cronbach's alpha")

@@

```{r ReplicabilityReliabilityTestTable, warning = FALSE}
# creating the dtaframe for the table
H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)

@@

# print the table in apa formatting
apa_table(
  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
  , caption = "Model Results from Tests of Hypothesis 3"
  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively. The random slope model for Cronbach's alpha did not converge, thus it results are not shown here. $^* p < .05$"
  , escape = FALSE, placement= "htp", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))

@@

```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by where each was coded from. The top row shows binned counts of QMP ratio’s that were observed for each replication protocol and original article, across the different QMP types. The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio. The specific observed values are indicated along the bottom row with dots"}
# plot for alpha
### ratio (REV) Original and Rep
Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
       aes(x = QMP_ratio, fill = RepOrg)) + 
  geom_bar(position = "dodge", stat = "bin", bins = 10) +
  facet_grid(~QMP_type) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_manual(values=c("brown", "blue4")) +
  theme(legend.position = "none") +
  ylab("Count") +
  xlab("QMP Ratio") +
  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

@@

```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line. The abbreviations on the axes relate to the QMP categories described in Table 1: Def. is definition, Op. is operationalization, Sel. is selection/creation, Quant. is quantification, and Mod. is modification. The X axis facets across the QMP ratios in the original articles, and the Y axis facets across the QMP ratios in the replication protocols. Each dot in the figure relates to describes the QMP ratio for the types in that graph across an original article and its replication protocol. Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
# Revised
ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

```{r H6ExploratoryAssociationsRevisedTable, warning = FALSE}
# creating the dataframe for the table
H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
  Results_H6_between_REV$sel_mod)

@@

# print the table in apa formatting
apa_table(
  H6_table_REV_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
  , caption = "Beta Regression Test Results for the Association between Replication
QMP Ratio and Original QMP Ratio as obtained using the Revised Protocol"
  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type. Sample size for comparisons involving modification were lower since not all measures were modified. Therefore the standard errors are larger. $^* p < .05$"
  , escape = FALSE, placement= "htp", midrules = c(1, 6, 7, 12, 13))

@@

```{r H6ExploratoryAssociationsInitialTable, warning = FALSE}
# creating the dataframe for the table
H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
  Results_H6_between$sel_mod)

@@

# print the table in apa formatting
apa_table(
  H6_table_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
  , caption = "Beta Regression Test Results for the Association between Replication
QMP Ratio and Original QMP Ratio as obtained using the Initial Protocol"
  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type. Sample size for comparisons involving modification were lower since not all measures were modified. Therefore the standard errors are larger. $^* p < .05$"
  , escape = FALSE, placement= "htp", midrules = c(1, 6, 7, 12, 13))

@@

```{r UnidimesnionalityTestResultsTable, warning = FALSE}
# add the names of the relevant papers and a shortcut for the measure used.
cfa_results_expanded <- cbind(c("Caruso et al. (2012)", "Husnu & Crisp (2010)", "Nosek et al. (2002), Art", "Nosek et al. (2002), Math", "Van Lange et al. (1997)", "Anderson et al. (2012), SWL", "Anderson et al. (2012), PA", "Anderson et al. (2012), NA", "Giessner & Schubert (2007)", "Norenzayan et al. (2002)", "Zhong & Liljenquist (2006)", "Monin & Miller (2001), most", "Monin & Miller (2001), some", "Cacioppo et al. (1983), elm", "Cacioppo et al. (1983), nfc", "De Fruyt et al. (2000), consc", "Albarracín et al. (2008), exp. 5", "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)

@@

# print the table in apa formatting
apa_table(
  cfa_results_for_print, align = c("l", "r", "r", "r")
  , caption = "RMSEA and Parallel Analysis Suggested Factors based on Factor Analysis
for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data. The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "htp")
